WORCS: A Workflow for Open Reproducible Code in Science

### 2020-11-03 paper/Manuscript_DS.Rmd
R1 C10 Fix url

The `worcs` package includes a [vignette on citation](https://cjvanlissa.github.io/worcs/articles/citing.html) to explain the
fundamentals for novice users, and offer recommendations specific to `worcs`. We
recommend using the free, open-source reference manager
[Zotero](https://www.zotero.org/download/); it is feature-rich, 
user-friendly, and highly interoperable with other reference managers. A 
tutorial for using Zotero with RMarkdown exists  [here](https://christopherjunk.netlify.com/blog/2019/02/25/zotero-RMarkdown/).

>>>>

The `worcs` package includes a [vignette on citation](https://cjvanlissa.github.io/worcs/articles/citation.html) to explain the
fundamentals for novice users, and offer recommendations specific to `worcs`. We
recommend using the free, open-source reference manager
[Zotero](https://www.zotero.org/download/); it is feature-rich, 
user-friendly, and highly interoperable with other reference managers. A 
tutorial for using Zotero with RMarkdown exists  [here](https://christopherjunk.netlify.com/blog/2019/02/25/zotero-RMarkdown/).

### 2020-11-03 paper/reviews_ds.Rmd
R1 C10 Fix url

\RC{Vignete on citation leads to a 404.}

>>>>

\RC{C10: Vignete on citation leads to a 404.}

Response: We apologize for the oversight; we have fixed this URL and checked all URLs in the manuscript for mistakes (none found).

<!--
check_urls <- function(x){
  #x = "C:/Git_Repositories/worcs/paper/manuscript_ds.Rmd"
  txt <- readLines(x)
  mtch <- regmatches(txt,regexpr("(http[^ ]*)|(ftp[^ ]*)|(www\\.[^ ]*)",txt))
  mtch <- gsub("[\\)\\.,;]+$", "", mtch)
  #out <- sapply(mtch, RCurl::url.exists)
  out <- sapply(mtch, httr::http_error)
}
-->
